Legion: Expressing Locality and Independence with Logical Regions

### 2012-04-30 doc/sc2012/circuit.tex

Lines 31-57 form the bulk of the actual simulation, performing three passes
over the circuit in each iteration.  Each pass loops over an array of pieces (constructed on lines 27-30 from the partitions),
spawning a task for each piece.   There are no explicit requests for
parallel execution (the default semantics of {\tt spawn} is sequential 
execution of the spawned tasks) nor is there synchronization required between the
passes.  Both the fact that the tasks can be run in parallel within a pass
and the required inter-pass dependencies are determined automatically
by the Legion runtime based on the region access annotations on the task declarations
(see Section~\ref{sec:soop}).

>>>>

Lines 31-57 form the bulk of the actual simulation, performing three passes
over the circuit in each iteration.  Each pass loops over an array of pieces (constructed on lines 27-30 from the partitions),
spawning a task for each piece.   There are no explicit requests for
parallel execution (the default semantics of {\tt spawn} is sequential 
execution of the spawned tasks) nor is there synchronization required between the
passes.  Both the fact that the tasks can be run in parallel within a pass
and the required inter-pass dependencies are determined automatically
by the Legion runtime based on the region access annotations on the task declarations.
The  tasks spawned on lines 32-34 are {\em subtasks} of the main
{\tt simulate\_circuit} task. The region arguments to a subtask  must be either regions of, or subregions of, the arguments to its parent task with a subset of the permissions and the same coherence properties.  This restriction plays a central role in our task scheduling algorithm (see Section~\ref{sec:soop}).
